\documentclass{letter}
\address{Pertersburgsgatan 14 Lgh 1202
\\ 302 47 Halmstad
\\ Sweden}

\signature{Mingkun Yang \\ Embedded \& Intelligent System major \\ albertnetymk@gmail.com \\ +46 764451122}


\begin{document}

\begin{letter}{ }
	%Embassy of Sweden
	%\\ Dongzhimenwai Dajie
	%\\ Chaoyang District, Sanlitun
	%\\ Beijing 100600}
	\opening{HR in HMS,}
	I'm writing to express my interest in the summer job, namely "Mjukvaruutvecklare Java", posted on your website. I have experience building one 
	compiler using Java, and some small projects related to various aspects of Java, such as concurrent programming, Swing development, etc.

	Since Java is the first OOP language I am exposed to, I use it as one medium to learn some OOP patterns from "Head First Patterns". In the 
	process of reading this book, I began to pick up the essence of real OOP development. I applied this to real development for my previous 
	part-time job, in which C\raise.2em\hbox{{\scriptsize\#}} is used along with ASP.NET MVC framework.

	I began to use Linux two years ago, and moved all my work to Linux afterwards. Meantime, I was following some lectures from CCNA about basic 
	network administration. I have never done real network administration, but I am ready to dive into it if necessary.

	Experience has taught me how to build strong relationship with others. I have the ability to work within a team as well as cross-team. Once I was 
	appointed to work on one project related to Ipad app development in the middle of development web applications, and the result is satisfying.

	I think I am prepared for this position. Thank you for your consideration.
	\closing{Yours Faithfully}
\end{letter}
\end{document}
