\documentclass[margin,line]{resume}
\usepackage{setspace}
\linespread{1}
\begin{document}
\name{\Large Mingkun Yang}
\begin{resume}
	\section{\mysidestyle Contact\\Information}
	C/O Albert Netymk													\hfill mobile: +46 764451122         \vspace{0mm}\\\vspace{0mm}%
	Pertersburgsgatan 14 Lgh 1202, 302 47 Halmstad						\hfill e-mail:  albertnetymk@gmail.com  \vspace{0mm}\\\vspace{-4.5mm}%
	                                                 

	\section{\mysidestyle Summary}
		Formal training in computer science and half year of hands on experience in developing software.
		Extensive embedded software programming knowledge and technical experience from low level software modules to high level software 
		applications.

	\section{\mysidestyle Research interests} 
		Code refactoring, software architecture design, TDD, Image processing, reading others' code\ldots

	\section{\mysidestyle Programming language} 
	C, C\raise.2em\hbox{{\scriptsize\#}}, Matlab, Java, Perl, JavaScript, CoffeeScript, Python, Bash

	\section{\mysidestyle General Computer Skills} 
		Linux administration, \LaTeX

	\section{\mysidestyle Education}

		\textbf{Halmstad University}, Halmstad, Halland, Sweden \vspace{2mm}\\\vspace{1mm}%
		\textsl{Masters in Embedded and Intelligent Systems} \hfill \textbf{ September 2011 -- present}\vspace{-3mm}\\\vspace{-1mm}%

		\textbf{Lanzhou University}, Lanzhou, Gansu, China \vspace{2mm}\\\vspace{1mm}%
		\textsl{Bachelors in Theoretical Physics} \hfill \textbf{ August 2007 -- July 2011}\vspace{-3mm}\\\vspace{-1mm}%

	\section{\mysidestyle Professional\\Experience}
		\textbf{Entergate}, Halmstad, Sweden \vspace{2mm}\\\vspace{1mm}%
		Developing one online survey web application.

		Developed one web application concerning Google map, enabling clients to mark interesting points and paths on the map.

	\section{\mysidestyle Thesis}
		Retrofitting Learning Management System to Use SCORM \\
		Extend one existing Learning Management System to use the SCORM standard using ASP NET MVC framework.

	\section{\mysidestyle Academic Projects}
		Title: Operating System on ARM
		Designed one small operating system, that supports scheduling and IPC, on ARM architecture.

		Title: Compiler Designing for minijava\\
		Designed a compiler for minijava(a subset of java) using compiler compiler and LLVM.

		Title: Parallel Computing in Ambric processor\\
		Got familiar with how to implement parallelism in this architecture.

		Title: E-commerce\\
		Constructed one e-commerce website using LAMP.

	\section{\mysidestyle Referees} 

	%\begin{tabular}{@{}p{6cm}p{6cm}}
	%	\textbf{Professor Tony Larsson}\\                          
	%	Professor of Embedded Systems\\
	%	Halmstad University\\                            
	%	Halmstad, Halland, Sweden   

	%	phone: \textsl{available on request}\\
	%	e-mail: \textsl{available on request}   
	%\end{tabular}
	\begin{tabular}{@{}p{6cm}p{6cm}}
		\textbf{}\\                          
		Nicolina Månsson\\
		Halmstad University\\                            
		Halmstad, Halland, Sweden\\
		Phone \textsl{+46 35 16 74 87}\\
		Email: \textsl{nicolina.mansson@hh.se}\\
	\end{tabular}
\end{resume}
\end{document}
